Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
final...

Then we found some extra states that never found when running only the subnets.
We figured out that is caused by a input mistake easily comparing it with the results on subnets.
\end{document}

>>>>

Analysing this result, we found some extra states that did not exist
when running only the subnets.
Comparing this with the previous result on on a single subnets, we
found that this was caused by a input mistake in a synchronisation vector.

After correction the algorithm produced 233280 OTs of which 281 are
satisfiable. The resulting automaton has 17 reachable states. Of
course we cannot display them here, and a model-checking tool would be
required for their formal analysis.

\end{document}
